Data-based completion of grey-box models with neural networks

### 2020-09-24 systemID_NNs.tex
ok.

\title{Data-based completion of grey-box models with neural networks}
\author{Problem formulation}
\date{\today}

@@

\textbf{Plant --}
\begin{align*}
  \dfrac{dC_A}{dt} &= \dfrac{C_{A0} - C_A}{\tau} - k_1C_A\\
  \dfrac{dC_B}{dt} &= k_1C_A - k_2C_B + k_3C_C- \dfrac{C_B}{\tau}\\
  \dfrac{dC_C}{dt} &= k_2C_B - k_3C_C - \dfrac{C_C}{\tau}
\end{align*}
These ODEs represent the dynamics of the reaction system
$A \rightarrow B \rightleftharpoons C$ in a CSTR with constant 
height and temperature. The control input is $u = C_{A0}$, 
and the measurements are $y = [C_A, C_B]'$. The plant model 
is observable with these choices of the measurements and dynamics.

\textbf{Model --}
\begin{align*}
  \dfrac{dC_A}{dt} &= \dfrac{C_{A0} - C_A}{\tau} - k_1C_A\\
  \dfrac{dC_B}{dt} &= k_1C_A - \dfrac{C_B}{\tau}
\end{align*}
i.e, we assume that we don't know about the second reaction while 
performing grey-box modeling.

>>>>

\title{Data-based completion of grey-box models with neural networks}
\author{Pratyush Kumar}
\date{\today}

@@

\textbf{Plant --}
\begin{align*}
  \dfrac{dC_A}{dt} &= \dfrac{C_{A0} - C_A}{\tau} - k_1C_A\\
  \dfrac{dC_B}{dt} &= k_1C_A - k_2C_B + k_3C_C- \dfrac{C_B}{\tau}\\
  \dfrac{dC_C}{dt} &= k_2C_B - k_3C_C - \dfrac{C_C}{\tau}
\end{align*}
These ODEs represent the dynamics of the reaction system
$A \rightarrow B \rightleftharpoons C$ in a CSTR with constant 
height and temperature. The control input is $u = C_{A0}$,
the states are $x = [C_A, C_B, C_C]'$, 
and the measurements are $y = [C_A, C_B]'$. The plant model 
is observable with these choices of the measurements and dynamics.

\textbf{Model --}
\begin{align*}
  \dfrac{dC_A}{dt} &= \dfrac{C_{A0} - C_A}{\tau} - k_1C_A\\
  \dfrac{dC_B}{dt} &= k_1C_A - \dfrac{C_B}{\tau}
\end{align*}
i.e, we assume that we don't know about the second reaction while 
performing grey-box modeling. Assume the following 
parameter choices $k_1 = 1 \ \textnormal{m}^3/\textnormal{min}, 
\ k_2 = 10^{-2} \ \textnormal{m}^3/\textnormal{min}
\ k_3 = 10^{-3} \ \textnormal{m}^3/\textnormal{min}$, 
and $\tau = 20 \ \textnormal{min}$.

Since the measurements are a simple linear function 
of the grey-box and plant states, we use only one network to 
augment the grey-box dynamics. The expected function 
to be approximated with a neural network is
\begin{align}
  f_{NN}(\mathbf{y}_{k:k-N}, \mathbf{u}_{k-1:k-N}) \approx (e^{A\Delta})^N
  \mathcal{O}(C, e^{A\Delta})^{\dagger}
\end{align}

\begin{figure}
  \centering
  \includegraphics[page=2, width=\textwidth]{tworeac_plots.pdf}
\end{figure}
